Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-27 paper.tex
add article to Cast ADT
Normalizing title case in section 4

\subsection{A Space-efficient CEK machine}
\label{sec:framework:cek}

%<<<<<<< HEAD
\effCEK{C} is a space-efficient CEK machine parameterized over Cast ADT ($C$).  
The key differences between \effCEK{C} and \ineffCEK\ are the places where 
casts can accumulate at runtime, that is, values and continuations. We discuss 
above the difference in values (Definition~\ref{def:values-effCEK}).

@@

\subsection{\effCEK{C} is equivalent to \ineffCEKD{}, provided $C$ is an instance of the Lazy D ADT}
\label{secc:framework:monoid-correct}

>>>>

\subsection{A Space-efficient CEK Machine}
\label{sec:framework:cek}

%<<<<<<< HEAD
\effCEK{C} is a space-efficient CEK machine parameterized over the Cast ADT ($C$).  
The key differences between \effCEK{C} and \ineffCEK\ are the places where 
casts can accumulate at runtime, that is, values and continuations. We discuss 
above the difference in values (Definition~\ref{def:values-effCEK}).

@@

\subsection{\effCEK{C} Is Equivalent to \ineffCEKD{}, Provided $C$ Is an Instance of the Lazy D ADT}
\label{secc:framework:monoid-correct}
